High-Fidelity Counterfactual Explanations through Conformal Prediction

### 2023-03-30 notebooks/intro.qmd
progress

measure = 
using CounterfactualExplanations.Evaluation: benchmark
bmks = []
for (dataname, dataset) in datasets
    bmk = benchmark(dataset; models=models, generators=generators, suppress_training=true, dataname=dataname)
    push!(bmks, bmk)
end
bmk = reduce(vcat, bmks)
```

@@

@@

temp = 0.5
p1 = contourf(mach.model, mach.fitresult, X, y; plot_set_loss=true, zoom=0, temp=temp)
p2 = contourf(mach.model, mach.fitresult, X, y; plot_classification_loss=true, target=1, zoom=0, temp=temp, clim=nothing, loss_matrix=ones(4,4))
plot(p1, p2, size=(800,320))
```

```{julia}
#| fig-cap: "Energy-based conditional samples."
#| label: fig-energy-multi

@@

```{julia}
counterfactuals = Dict([name => generate_counterfactual(x, target, counterfactual_data, M, gen; initialization=:identity, converge_when=:generator_conditions, gradient_tol=1e-3) for (name, gen) in generators])

>>>>

```{julia}
#| output: false
using CounterfactualExplanations.Evaluation: benchmark
bmks = []
for (dataname, dataset) in datasets
    bmk = benchmark(dataset; models=models, generators=generators, suppress_training=true, dataname=dataname)
    push!(bmks, bmk)
end
bmk = reduce(vcat, bmks)
```

@@

```{julia}
X = table(permutedims(counterfactual_data.X))
y =  counterfactual_data.output_encoder.labels
conf_model = conformal_model(clf; method=:simple_inductive, coverage=0.99)
mach = machine(conf_model, X, y)
fit!(mach)
```

@@

temp = 0.05
p1 = contourf(mach.model, mach.fitresult, X, y; plot_set_loss=true, zoom=-1, temp=temp)
p2 = contourf(mach.model, mach.fitresult, X, y; plot_classification_loss=true, zoom=-1, temp=temp, clim=nothing, loss_matrix=ones(4,4))
plot(p1, p2, size=(800,320))
```

```{julia}
#| output: true
#| echo: false
#| fig-cap: "Energy-based conditional samples."
#| label: fig-energy-multi

@@

```{julia}
#| output: true
#| echo: false
#| fig-cap: "Comparison of counterfactuals produced using different generators."
#| label: fig-ce-multi
